---
title: "SPMC 350 Flashcards"
output: html_notebook
---

This notebook serves as a companion to the [SPMC 350 Sports Data Tutorials](https://github.com/mattwaite/SportsDataTutorials) and/or the [SPMC 350 Sports Data Book](http://mattwaite.github.io/sports/).

It uses the [`flashr`](https://github.com/JeffreyRStevens/flashr) library. 

First load the `flashr` library.

```{r}
library(flashr)
```

Each of these corresponds to a chapter:

## Basics

```{r}
flashcard("data/basics.csv")
```

## Data basics

```{r}
flashcard("data/data_basics.csv")
```

## Aggregates

```{r}
flashcard("data/aggregates.csv")
```

## Mutating

```{r}
flashcard("data/mutating.csv")
```

## Filtering

```{r}
flashcard("data/filtering.csv")
```

## Transforming

```{r}
flashcard("data/transforming.csv")
```

## Significance tests

```{r}
flashcard("data/significancetests.csv")
```


### Credits

Stevens, Jeffrey R. (2022). flashr: Creates flashcards of terms and definitions. (version 0.0.2) https://github.com/JeffreyRStevens/flashr
